---
title: "Make your figures here"
author: "Katherine Heal"
date: "January 10 2020"
output: html_document
---
#TO DO: fix the names!!
#TO DO: check and remake with R 4.0
```{r setup, include=FALSE}
library(tidyverse)
```

#Quantifiable compounds, Bar plots
```{r, error = FALSE, warning=FALSE, message=FALSE}
#mol fraction C
source('Figures/Code/BarPlots_molPerCent_C.R')
remove(list = ls())

#mol fraction N
source('Figures/Code/BarPlots_molPerCent_N.R')
remove(list = ls())

#nmole C
source('Figures/Code/BarPlots_nMolC.R')
remove(list = ls())

#nmol N
source('Figures/Code/BarPlots_nMolN.R')
remove(list = ls())

```

#Summary box plots
```{r, error = FALSE, warning=FALSE, message=FALSE}
#nmol C
source('Figures/Code/Summary_boxPlot.R')
remove(list = ls())
```

#NMDS
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/NMDS_untargeted.R')
remove(list = ls())
detach("package:MASS", unload=TRUE)
```

#Mode plots for each of the sample sets
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/multi_panel_mode.R')
remove(list = ls())

source('Figures/Code/multi_panel_culture.R')
remove(list = ls())
```

#Tile alluvial plot for KOK and orgs :) 
Remake and reload
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/KOK_org_AlluvialPlot.R")
remove(list = ls())
```

#PC plot 
```{r, error = FALSE, warning=FALSE, message=FALSE}
#PC plot
source("Figures/Code/PCPN_latitude.R")
```


#Nonessential
Pigments, lugols, and PC plots
```{r, error = FALSE, warning=FALSE, message=FALSE}
#HPLC plot (saved in prelim)
source("Figures/Code/HPLC_latitude.R")

#Lugols plot (saved in prelim)
source("Figures/Code/Lugols_latitude.R")
remove(list = ls())

```






#Mode plots for the clusters of compounds in the environmental samples
#Mode plots for different sample sets

#Alluvial plot with organisms and environmental samples

