---
title: "Make your figures here"
author: "Katherine Heal"
date: "January 10 2020"
output: html_document
---
Figures for Gradients 1.0 metabolomics manuscript and associated presentations

TO DO: fix the names!!

```{r setup, include=FALSE}
library(tidyverse)
```


#Quantifiable compounds, Bar plots
```{r, error = FALSE, warning=FALSE, message=FALSE}
#mol fraction C
source('Figures/Code/BarPlots_molPerCent_C.R')
remove(list = ls())

#mol fraction N
source('Figures/Code/BarPlots_molPerCent_N.R')
remove(list = ls())

#nmole C
source('Figures/Code/BarPlots_nMolC.R')
remove(list = ls())

#nmol N
source('Figures/Code/BarPlots_nMolN.R')
remove(list = ls())

```

#Summary box plot
```{r, error = FALSE, warning=FALSE, message=FALSE}
#nmol C
source('Figures/Code/Summary_boxPlot.R')
remove(list = ls())
```

#NMDS for KOK samples and for organisms!
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/NMDS_untargeted.R')
remove(list = ls())
detach("package:vegan", unload=TRUE)
detach("package:MASS", unload=TRUE)


source('Figures/Code/NMDS_orgs.R')
detach("package:vegan", unload=TRUE)
detach("package:MASS", unload=TRUE)
```

#Mode plots for each of the sample sets
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/multi_panel_mode.R')
remove(list = ls())

source('Figures/Code/multi_panel_culture.R')
remove(list = ls())
```

#Tile alluvial plot for KOK and orgs :) 
TO DO: fix up the colors
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/KOK_org_AlluvialPlot.R")
remove(list = ls())
```

#PC plot 
```{r, error = FALSE, warning=FALSE, message=FALSE}
#PC plot
source("Figures/Code/PCPN_latitude.R")
remove(list = ls())
```

#Plot of ug/ug C field vs 
Still very prelim
#TO DO: check if Nmar data are being included
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/FieldvsCulture_CComparison.R")
remove(list = ls())
```

#Plot homarine and trigonolline
#TO DO: make it so the organisms' contributions are
```{r}
source("Figures/Code/Homarine.R")
remove(list = ls())
```

#Plot of stacked bars in cultures
```{r}
source("Figures/Code/Orgs_stackedbars.R")
remove(list = ls())
```

#Plot of DSS-3 growth curves
```{r}
source("Figures/Code/DSS3_growthcurves.R")
remove(list = ls())
```








#Nonessential
Pigments, lugols, and PC plots
```{r, error = FALSE, warning=FALSE, message=FALSE}
#HPLC plot (saved in prelim)
source("Figures/Code/HPLC_latitude.R")

#Lugols plot (saved in prelim)
source("Figures/Code/Lugols_latitude.R")
remove(list = ls())

```






#Mode plots for the clusters of compounds in the environmental samples
#Mode plots for different sample sets

#Alluvial plot with organisms and environmental samples

