---
title: "Make your figures here"
author: "Katherine Heal"
date: "January 10 2020"
output: html_document
---
Figures for Heal *et. al* manuscript and associated presentations

```{r setup, include=FALSE}
library(tidyverse)
```

# Mode plot with map, network plot
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/modes_and_nodes_2plots.R')
remove(list = ls())
```

# Tile alluvial plot for KOK and orgs  
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/KOK_org_AlluvialPlot.R")
remove(list = ls())
```

# Quantifiable compounds in environmental sampls, stacked bar plot
```{r, error = FALSE, warning=FALSE, message=FALSE}
#mol fraction C (main text figure)
source('Figures/Code/BarPlots_molPerCent_C.R')
remove(list = ls())
```

# Plot of homarine and trigonolline over space and in organisms
```{r}
source("Figures/Code/Homarine.R")
remove(list = ls())
```

# Plot of stacked bars in cultures
```{r}
source("Figures/Code/Orgs_stackedbars.R")
remove(list = ls())
```









# Combine stacked bar nMolC with arsenobetaine with inset
```{r}
#nmole C (supplemental figure)
source('Figures/Code/BarPlots_nMolC.R')
remove(list = ls())

```

# Summary box plot
```{r, error = FALSE, warning=FALSE, message=FALSE}
#nmol C
source('Figures/Code/Summary_boxPlot.R')
remove(list = ls())
```

# NMDS for transect environmental samples and for organisms
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/NMDS_untargeted.R')
rm(list=setdiff(ls(), "d"))

source('Figures/Code/NMDS_orgs.R')
rm(list=setdiff(ls(), c("d.raw", "d")))
detach("package:vegan", unload=TRUE)
detach("package:MASS", unload=TRUE)

source('Figures/Code/NMDS_combine.R')
remove(list = ls())
```




##To do combine these:
# PC plot (PC over transect, with total quantifiable metabolites)
```{r, error = FALSE, warning=FALSE, message=FALSE}
#PC plot
source("Figures/Code/PCPN_latitude.R")
remove(list = ls())
```

# Fucoxanthin over space
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/Fuxo_by_latitude.R")
remove(list = ls())
```

# Seaflow by latitude (numbers and carbon)
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/SeaFlowC_byLat.R")
remove(list = ls())
```




## These are good to go
# Plot of ug/ug C field vs organisms
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/FieldvsCulture_CComparison.R")
remove(list = ls())
```

# Plot of DMS-Ac and gonyol over space and in organisms
```{r}
source("Figures/Code/Gonyol_DMSAc.R")
remove(list = ls())
```

# Plot of DSS-3 growth curves
```{r}
source("Figures/Code/DSS3_growthcurves.R")
remove(list = ls())
```





