---
title: "Make your figures here"
author: "Katherine Heal"
date: "January 10 2020"
output: html_document
---
Figures for Heal *et. al* manuscript and associated presentations

```{r setup, include=FALSE}
library(tidyverse)
```

# Mode plot with map, network plot
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/modes_and_nodes_2plots.R')
remove(list = ls())
```

# Tile alluvial plot for KOK and orgs  
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/KOK_org_AlluvialPlot.R")
remove(list = ls())
```


# Quantifiable compounds in environmental sampls, Stacked bar plots
```{r, error = FALSE, warning=FALSE, message=FALSE}
#mol fraction C
source('Figures/Code/BarPlots_molPerCent_C.R')
remove(list = ls())

#mol fraction N
source('Figures/Code/BarPlots_molPerCent_N.R')
remove(list = ls())

#nmole C
source('Figures/Code/BarPlots_nMolC.R')
remove(list = ls())

#nmol N
source('Figures/Code/BarPlots_nMolN.R')
remove(list = ls())

```

# Summary box plot
```{r, error = FALSE, warning=FALSE, message=FALSE}
#nmol C
source('Figures/Code/Summary_boxPlot.R')
remove(list = ls())
```

# NMDS for transect environmental samples and for organisms
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Code/NMDS_untargeted.R')
remove(list = ls())
detach("package:vegan", unload=TRUE)
detach("package:MASS", unload=TRUE)


source('Figures/Code/NMDS_orgs.R')
detach("package:vegan", unload=TRUE)
detach("package:MASS", unload=TRUE)
```


# PC plot (PC over transect, with total quantifiable metabolites)
```{r, error = FALSE, warning=FALSE, message=FALSE}
#PC plot
source("Figures/Code/PCPN_latitude.R")
remove(list = ls())
```

# Plot of ug/ug C field vs organisms
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/FieldvsCulture_CComparison.R")
remove(list = ls())
```

# Plot of homarine and trigonolline over space and in organisms
```{r}
source("Figures/Code/Homarine.R")
remove(list = ls())
```

# Plot of DMS-Ac and gonyol over space and in organisms
```{r}
source("Figures/Code/Gonyol_DMSAc.R")
remove(list = ls())
```

# Plot of arsenobetaine and beta-glutamic acid over depth
```{r}
source("Figures/Code/Beta-glutamic.R")
remove(list = ls())
```

# Plot of stacked bars in cultures
```{r}
source("Figures/Code/Orgs_stackedbars.R")
remove(list = ls())
```

# Plot of DSS-3 growth curves
```{r}
source("Figures/Code/DSS3_growthcurves.R")
remove(list = ls())
```

# Fucoxanthin over space
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/Fuxo_by_latitude.R")
remove(list = ls())
```

# Seaflow by latitude (numbers and carbon)
```{r, error = FALSE, warning=FALSE, message=FALSE}
source("Figures/Code/SeaFlow_by_latitude.R")
remove(list = ls())

source("Figures/Code/SeaFlowC_byLat.R")
remove(list = ls())
```




